Reconstructing the Lensing Mass in the Universe \\ from Photometric Catalogue Data

### 2013-03-01 doc/paper-lcr.tex
added section on SM-HM relation

We test the potential size of this systematic error by using the \citet{BehrooziEtal2010} relation to generate the stellar masses of our calibration lines of sight, but the Stellar Mass--Halo Mass relation of \citet{MosterEtal2010} for the 'real' lines of sight that are reconstructed.

@@

Applying our Behroozi--based reconstruction to lines of sight with Moster stellar masses results in systematically overestimating $\kappax$. In \Fref{fig:SHAMbias} we show the resulting bias on the inferred $\kappax$ after combining several lines of sight. With a purely photometric reconstruction there is a typical systematic bias of $\sim 0.025$ on the reconstructed convergence, although it can be shrunk to $\sim 0.01$ if only the low $\kappax$ lines of sight are used, however for the high shear lines of sight the bias is $\sim 0.04$. It is not suprising that the low $\kappax$ lines of sight are least affected by changes in the stellar mass--halo mass relation. Low $\kappax$ lines of sight are relatively empty hence their $\kappah$ values are small and do not change significantly with stellar mass--halo mass relation. The high shear lines of sight have significantly overestimated $\kappax$ since they tend to lie close to massive halos. This is the regime where the Moster and Behroozi relations are most different.

Despite the systematic errors the photometric reconstruction is still sufficient to choose the best lines of sight for spectroscopic follow-up. With targetted spectroscopy the systematic error decreases to $\sim 0.014$ for the ensemble, $\sim 0.005$ for the low kappa sample and $\sim 0.018$ for the high shear sample. 
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

We test the potential size of this systematic error by using the \citet{BehrooziEtal2010} relation to generate the stellar masses of our calibration lines of sight, but the stellar mass--halo mass relation of \citet{MosterEtal2010} for the \"real\" lines of sight that are reconstructed.

@@

Applying our Behroozi--based reconstruction to lines of sight with Moster stellar masses results in systematically overestimating $\kappax$. In \Fref{fig:SHAMbias} we show the resulting bias on the inferred $\kappax$ after combining several lines of sight. With a purely photometric reconstruction there is a typical systematic bias of $\sim 0.025$ on the reconstructed convergence, although it can be shrunk to $\sim 0.01$ if only the low $\kappax$ lines of sight are used, however for the high shear lines of sight the bias is $\sim 0.04$. It is not suprising that the low $\kappax$ lines of sight are least affected by changes in the stellar mass--halo mass relation. Low $\kappax$ lines of sight are relatively empty hence their $\kappah$ values are small and do not change significantly with stellar mass--halo mass relation. The high shear lines of sight have significantly overestimated $\kappax$ since they tend to lie close to massive halos. This is the regime where the Moster and Behroozi relations are most different. Interestingly overestimating the $\kappah$ values of high shear lines of sight pushes them into the region where the $\kappah$ to $\kappax$ calibration is least certain; this has significantly decreased the precision of the reconstructed $\kappax$.

Despite the systematic errors the photometric reconstruction is still sufficient to choose the best lines of sight for spectroscopic follow-up. With targetted spectroscopy the systematic error decreases to $\sim 0.014$ for the ensemble, $\sim 0.005$ for the low kappa sample and $\sim 0.018$ for the high shear sample. This result provides further motivation for prioritizing the lenses that reside on the underdense lines of sight.
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
